---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# appMaker

<!-- badges: start -->
<!-- badges: end -->

The goal of appMaker is to create apps with the Hamilton Institute Distill theme.

## Installation

You can install the appMaker from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("hamilton-institute/appMaker")
```

## Creating a simple app

To create a simple app you need to run:

```{r,eval=FALSE}
library(appMaker)

create_simple_app(path = "~/Desktop/myApp")
```

The code above will create a RStudio project called `myApp` at your Desktop folder (change the path to a existing folder if you don't have a Desktop folder). A new RStudio session will open automatically with this project open.

The created project has a placeholder app in the `app.R` file. To create your app, you need to modify the `ui` object and `server` function in this file. If you want to keep the Distill theme, do not remove the `hamiltonThemes::` functions.


## Creating a dashboard

To create a dashboard you need to run:

```{r,eval=FALSE}
library(appMaker)

create_dash(path = "~/Desktop/myDashboard")
```

The code above will create a RStudio project called `myDashboard` at your Desktop folder (change the path to a existing folder if you don't have a Desktop folder). A new RStudio session will open automatically with this project open.

The created project has a placeholder [golem shiny app](https://github.com/ThinkR-open/golem). Golem uses [shiny modules](https://shiny.rstudio.com/articles/modules.html), so you have the modify the `app_ui.R`, `app_server.R` and all `mod_.R` files to create your app.

A golem shiny app is a R package, what is great to develop any app with too many lines of code. To run the app, run `devtools::load_all()` to load all functions at R folder. After that, run the `run_app()` function in the Console. 

If you want to keep the Distill theme, do not remove the `hamiltonThemes::` functions.



